Experimenting with n-grams in Civil Procedure Codes

### 2014-08-14 experiment.Rmd
Omitting some unnecessary, buggy code

---
title: "Experimenting with n-grams in Civil Procedure Codes"
author: "Kellen Funk"
date: "August 4, 2014"
output: html_document
---

@@

```{r}
comparison_of_matches <- sample_matches %>% lapply(., kwic_ngram_match,
                          codes_texts$NY1850.txt,
                          codes_texts$NC1868.txt,
                          disp_chars = 300) %>%
                            do.call(rbind.data.frame, .)
comparison_of_matches
write.csv(comparison_of_matches, file = "out/matches_ny_nc_kwic.csv")
```

@@

```{r, fig.height = 3, fig.width = 8}
density_plot_color <- rgb(0.5, 0.5, 0.5, 0.1)
ca_matches <- codes_grams$NC1868.txt %in% cf_ny_nc$matches  
ca_matches %>% 
  plot(type = "h",
       col = density_plot_color,
       ann = FALSE,
       yaxt = "n",
       xaxt = "n")
title("Places in CA 1851 Code with Matches in NY 1850 Code",
      xlab = "Position in code",
      ylab = "")
```
```

>>>>

---
title: "Experimenting with n-grams in Civil Procedure Codes"
author: "Kellen Funk"
output: html_document
---

@@

```{r}
# TEMPORARILY REMOVED
# comparison_of_matches <- sample_matches %>% lapply(., kwic_ngram_match,
#                           codes_texts$NY1850.txt,
#                           codes_texts$NC1868.txt,
#                           disp_chars = 300) %>%
#                             do.call(rbind.data.frame, .)
# comparison_of_matches
# write.csv(comparison_of_matches, file = "out/matches_ny_nc_kwic.csv")
```

@@

```{r, fig.height = 3, fig.width = 8}
density_plot_color <- rgb(0.5, 0.5, 0.5, 0.1)
ca_matches <- codes_grams$CA1851.txt %in% cf_ny_ca$matches  
ca_matches %>% 
  plot(type = "h",
       col = density_plot_color,
       ann = FALSE,
       yaxt = "n",
       xaxt = "n")
title("Places in CA 1851 Code with Matches in NY 1850 Code",
      xlab = "Position in code",
      ylab = "")
```
